Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-07-12 Tex/Paper.tex
Additions

The preliminary design of AWAKE Run 2 proposes to use two plasma sections. The first section of 4m is the SMI stage. The
electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur. As the
$e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible
\cite{adli:2016}.

@@

% ******************************************************************************************************************** %
\subsection[\label{S:M:Setup}]{Drive Beam Parameters}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\section[\label{S:BL}]{Beam Loading}
%~ Eric's Comments
%~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
% ******************************************************************************************************************** %

@@

The structure of the single drive beam setup behaves similarly to the self-modulated case. However, since the drive
beam is prevented from significant evolution in this simulation setup, we are presented with an idealised case where
the electron witness beam sees consistent fields.

>>>>

The preliminary design of AWAKE Run 2 proposes to use two plasma sections. The first section of 4m is the SMI stage. The
electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur. As the
$e_z$ field will decrease due to the gap between the two cells, it is desirable to keep this as short as possible
\cite{adli:2016}.

% ******************************************************************************************************************** %
\subsection[\label{S:I:SMI}]{Self-modulation as a Driver}
%~ Patric's Comments
%~ - Self-modulation as a driver
%~ - SM does not reach blow out
%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
%~   not desirable
% ******************************************************************************************************************** %

A train of electron drive bunches with a separation $\lambda_{p}$ and a length $l_{b} \ll \lambda_{p}$, where
$\lambda_{p} = 2\pi c/\omega_{p}$ and $\omega_{p} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$, will drive an
increasingly strong field $E_{z}$ for each bunch \cite{chen:1985}. A tailing witness beam loading the peak accelerating
phase of this field will quickly gain energy from the wakefield. However, electron drive bunches will quickly lose
energy to the plasma, and the accelerating witness beam will eventually catch up with the drive beam and the
acceleration stop.

The de-phasing problem can be minimised by instead using a proton drive bunch \cite{caldwell:2009}. Proton beams, like
the LHC and SPS beams at CERN, are ideal candidates for such an accelerator; however, they are orders of magnitude
longer than the plasma wavelengths needed for such applications. This issue is resolved by letting the proton beam
undergo self-modulation, an instability caused by the transverse fields generated by the beam acts upon itself causing
regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency is close to that of the plasma,
leaving a train of proton bunches along the beam axis.

The AWAKE experiment currently in its first stages of operation at CERN, uses the SPS beam as its driver. The experiment
is set up with a $10\unit{m}$ rubidium plasma cell, with a nominal plasma density of $7\nexp{14}\unit{cm}^{-3}$.

@@

% ******************************************************************************************************************** %
\subsection[\label{S:M:Setup}]{Drive Beam Parameters}
%~ Patric's Comments
%~ - Self-modulation as a driver
%~ - SM does not reach blow out
%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
%~   not desirable
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\section[\label{S:BL}]{Beam Loading}
%~ Eric's Comments
%~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
%~
%~ Patric's Comments
%~ - Beam loading for narrow energy spread
%~ - Beam loading in linear regime (old papers from SLAC in the 80's, then Katsouleas for PWFA) and nonlinear regime
%~   (Tzoufras) well know
%~ - Propose "new regime" in the SM case, beam loading and blowout to get emittance preservation
%~ - Limitation as for PWFA driver, must use some of the W bunch to reach the blowout, it is kind of like the early SLAC
%~   experiments (84GeV) where the W-bunch is like the D-bunch in these experiments, but in a plasma prepared by the p+
%~   bunch and the SM
%~ - maybe also something about the fact that 200pC in a 60µm bunch corresponds to a 1kA current, much larger than the
%~   p+ bunch current, because of the fact that the wakefields are driven my multiple bunches?
% ******************************************************************************************************************** %

@@

The single drive beam setup is designed to behave similarly to the self-modulated case. However, since the drive beam is
prevented from significant transverse evolution, we are presented with an idealised case where the electron witness beam
sees consistent fields. The
